Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-08-20 latex/ms.tex
add new subsection for explation of extension of the model, 2.8,#7

\subsection{Parent number can be estimated by PO pairs found within a population}

@@

>>>>

\subsection{Estimation of parent number by PO pairs found within a population}

@@

Table \ref{parameter} summarizes the conditions for estimators appeared in this paper as to whether $N_1$ and/or $N_2$ are known and which type of samples are needed for estimation, and provides required kinship type for calculating the estimator.

\subsection{Variation in reproductive potential among individuals and populations}

\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
